---
title: "Artificial Hydrocarbon Networks in R"
author: "Jose Roberto Ayala Solares"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ahnr_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

`ahnr` is a package that implements the artificial hydrocarbon networks developed by [Hiram Ponce](http://www.up.edu.mx/es/investigador/25611/hiram-eredin-ponce-espinosa-dr). Most of the work is based on the book [Artificial Organic Networks](http://www.springer.com/gb/book/9783319024714).

## Quick Start

Here are some quick examples to get you started.

## Create a network for a SISO sytem

The following code let's you create the data to train an artificial hydrocarbon network.

```{r Example 1 Training}
library(ahnr)

# Create data
set.seed(12321)
x <- 2 * runif(1000) - 1;
x <- sort(x)

y <- (x < 0.1) * (0.05 * runif(100) + atan(pi*x)) + 
    (x >= 0.1 & x < 0.6) * (0.05 * runif(1000) + sin(pi*x)) + 
    (x >= 0.6) * (0.05 * runif(1000) + cos(pi*x))

plot(x, y, type = 'l')

# Create the Sigma dataset
Sigma <- list(X = data.frame(x = x), Y = data.frame(y = y))

# Create network
ahn <- AHNnD(Sigma, 5, 0.01, 1000)
```

The trained network can be used to visualize its performance.

```{r Example 1 Simulation}
# Create test data
X <- data.frame(x = x)

# Simulate
ysim <- SimAHNnD(ahn, X)

plot(x, y, type = 'l')
lines(x, ysim, type = 'l', col = 'red')
```

A summary of the network can be obtained with the `summary` command.

```{r Example 1 Summary}
summary(ahn)
```

Finally, the network itself can be plotted with the `plot` command.

```{r Example 1 Network Visualization}
plot(ahn)
```


## Create a network for a MISO sytem

```{r}
# Create data
t <- seq(0, 15, 0.01)
X <- data.frame(x1 = cos(t), x2 = t)
Y <- data.frame(y = sin(t))

# Create the Sigma dataset
Sigma <- list(X = X, Y = Y)

# Create network
ahn <- AHNnD(Sigma, 5, 0.01, 500)

# Simulate
ysim <- SimAHNnD(ahn, X)

plot(seq_along(Y$y), Y$y, type = 'l', col = 'black')
lines(seq_along(ysim), ysim, col = 'red')
```

```{r Example 2 Summary}
summary(ahn)
```

```{r Example 2 Network Visualization}
plot(ahn)
```
